---
title: "Shiny Tutorial"
author: "Michael McCormack"
date: "March 27, 2018"
output: pdf_document 
---

```{r setup, include=FALSE}
suppressMessages(require(tidyverse))
install.packages("shiny")
library(shiny)
```

## Step 1: Create an initial outline of your Shiny app
This can either be one file called app.R or 2 files called 1 being ui.R and the other being server.R.  

```{r}

library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   titlePanel("Old Faithful Geyser Data"),
   
   # Sidebar with a slider input for number of bins 
   sidebarLayout(
      sidebarPanel(
         sliderInput("bins",
                     "Number of bins:",
                     min = 1,
                     max = 50,
                     value = 30)
      ),
      
      # Show a plot of the generated distribution
      mainPanel(
         plotOutput("distPlot")
      )
   )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
   
   output$distPlot <- renderPlot({
      # generate bins based on input$bins from ui.R
      x    <- faithful[, 2] 
      bins <- seq(min(x), max(x), length.out = input$bins + 1)
      
      # draw the histogram with the specified number of bins
      hist(x, breaks = bins, col = 'darkgray', border = 'white')
   })
}

# Run the application 
shinyApp(ui = ui, server = server)



```

## Step 2: Incorporate our data into the app
Here we will use flight data for a single month.

We want to compare the percentage of flights delayed on a certain to the total percentage of flights delayed for this month (January 2017).


Use the flights data from our previous project to display in Shiny form.  This is generally done in the server.R file.

```{r}
##Example of Server.R file
library(shiny)

# EDA before visualization
data <- read.csv("2017FL_performance.csv")

data %>% drop_na()

data %>% 
  select(DAY_OF_MONTH,ARR_DELAY,DEP_DELAY,CANCELLED) %>% 
  group_by(DAY_OF_MONTH) %>%
  summarise(avg_dep_delay = mean(DEP_DELAY, na.rm = TRUE),
            avg_arr_delay = mean(ARR_DELAY, na.rm = TRUE),
            avg_cancel = mean(CANCELLED))
            
      

colnames(data)[1] <- "days"



# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   titlePanel("Flight Data"),
   
   # Sidebar with a slider input for number of bins 
   sidebarLayout(
      sidebarPanel(
         sliderInput("bins",
                     "Number of bins:",
                     min = 1,
                     max = 50,
                     value = 30)
      ),
      
      # Show a plot of the generated distribution
      mainPanel(
        tabsetPanel(type = "tabs",
        tabPanel("Gender", plotOutput("distPlot")),
        tabPanel("Job",plotOutput("job"))))
      )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
   
   output$distPlot <- renderPlot({
      # generate bins based on input$bins from ui.R
      x    <- faithful[, 2] 
      bins <- seq(min(x), max(x), length.out = input$bins + 1)
      
      # draw the histogram with the specified number of bins
      hist(x, breaks = bins, col = 'darkgray', border = 'white')
   })
}

# Run the application 
shinyApp(ui = ui, server = server)



```

## Step 3: Have the app Visualize this data using Barcharts:
Advanced - do this in ggplot

## Step 4: Make sure the app is interpretable
Label axis, Title, quick description of what you're visualizing

## Step 5:  Add a new tab:


## Step 6: Locate all the cities on a geograpical map
